resistanceModelNotesAndy

### 2016-01-14 resistanceModelNotesAndy.Rmd
notes

9/1/16 on train back from liverpool game rollout workshop

@@

13/1/16
starting on the new 1 parameter at a time sensi analysis in sensiAnPaperPartOneAtATime.r

@@

@@

1. is there a way I can easily run single & combined deployments for the same scenario ?
* is it `niche_00` and `niche_AB`
* or in `a.m_AB` insecticide exposure male hi1 hi2
* do I also need to change "Starting frequency of resistance" ?
* perhaps I can set up a simple example input to send to Beth ?
* or ask Beth to send me the input.csv used to produce tables 8 & 9 in 'Brief_full-genotype-tables.pdf'
* maybe comparing the files in full-dom_CD.csv & SD in C:\Dropbox\Levick et al IR manuscript will help me.

@@

### refactoring variables to arrays ?
Refactoring to arrays will reduce code volume, reduce risk of mistyped variable names and allow objects to be passed between functions.
cis/trans makes it slightly tricky, but not all variables have cis/trans
only used for genotype frequencies (f) and in output matrices fitness & genotype 
in the wild in Beths code :
```
fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
```

@@

** A, B, a, b, -** 2 insecticides at 3 levels; low(ab), high(AB), absent(--) resulting in 9 niches.

Locus1 relates to resistance for insecticide A, and locus2 for B. Locus2 does not effect exposure to A.

>>>>

** 9/1/16 ** on train back from liverpool game rollout workshop

@@

** 13/1/16 **
starting on the new 1 parameter at a time sensi analysis in sensiAnPaperPartOneAtATime.r

** 14/1/16 **
first see if I can make any informative plots with the existing sensitivity analysis data

These outputs are the frequencies by generation of the resistance alleles for the different insecticides (1&2) 
Gen, m.R1, m.R2, f.R1, f.R2

I want to get to a single file that has inputs & time_to_resistance thresholds for each scenario.

I must have something nearly like this already from sensiAnPaper1All.Rmd

Yes : resistPointsI1,2,Mix etc.
For each scenario these have gen_cP0.1,0.25,0.5 which is the number of generations taken to reach those resistance thresholds.

The next chunk works out which strategy is better than which.

Maybe I want to bind all the resistPoints together into one file and bind onto the inputs, so that we can look at how the inputs effect the time to resistance for the different strategies.

I want input on the x axis & time to resistance on the y. (but there will be the issue that the y values will be affected by the changing values of other parameters too) Cross that bridge when I come to it.

how to get data in format for ggplot2
check the diamonds dataset in ggplot2

so I want to get as a dataframe with scenarios in rows, & columns for inputs & outputs

so I can do something like :
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point()

If I have a column that is strategy (insecticide1, insectide2, sequential, mixture)
Then I would be able to facet by these later.

ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point() + facet_wrap( ~ cut)

This could be good as I can see the different strategies side by side.

So I want columns :
input1, input2 ... strategy, outputs : gen_cP0.1, 0.25, 0.5

so the dataframe will have length=num strategies*num scenarios

I'll need to rbind the strategies on top of each other.

Some success with ggplot plots.

@@

Files :
listOut* I1,I2, Mix : raw results for insecticide1,2 & mixture
                    : results are in $results[[scenarioNum]]
                    : e.g. listOutI1$results[[1]] has columns
                    : colnames(listOutI1$results[[1]])
                    : "Gen" "m.R1" "m.R2"  "m.LD" "f.R1"  "f.R2" "f.LD" "M"  "F"  "dprime" "r2"
treeInput : a matrix with scenarios in columns, inputs & outputs in rows

@@

@@

### refactoring variables to arrays
Refactoring to arrays reduces code volume, reduces risk of mistyped variable names and allow objects to be passed between functions.
cis/trans makes it slightly tricky, but not all variables have cis/trans
only used for genotype frequencies (f) and in output matrices fitness & genotype 
in the wild in Beths code :
```
fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
```

@@

** A, B, a, b, -** 2 insecticides at 3 levels; low(ab), high(AB), absent(--) resulting in 9 niches.  
Locus1 relates to resistance for insecticide A, and locus2 for B. Locus2 does not effect exposure to A.
